
# Chapter 2. The Heckscher-Ohlin Model

In these exercises, you will reproduce some of the empirical results from Trefler (1993, 1995).  To complete the exercise, the Excel file `hov_pub.csv` should be stored in the directory:
`c:\Empirical_Exercise\Chapter_2\hov_pub.csv`.  After this, run the STATA program `hov_pub.do`, which will create a new STATA data file `trefler.dta`.

## Read and transform the data

### Feenstra's code

```stata
* This is to read the data into Stata *

set mem 30m
* insheet using c:\Empirical_Exercise\Chapter_2\trefler.csv *
insheet using "Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-2\hov_pub.csv"
rename v1 country
rename v2 factor
rename v3 AT
rename v4 V
rename v5 Y
rename v6 B
rename v7 YPC
rename v8 POP

* create country index *
quietly summarize YPC
local maxYPC=_result(6)
gen ratio=YPC/`maxYPC'
replace ratio=ratio+0.0001 if country=="Italy"

sort ratio
egen indexc=group(ratio)

* create factor index *
sort factor
egen indexf=group(factor)

* include delta *

gen delta=1
replace delta=0.03 if country=="Bangladesh"
replace delta=0.09 if country=="Pakistan"
replace delta=0.10 if country=="Indonesia"
replace delta=0.09 if country=="Sri Lanka"
replace delta=0.17 if country=="Thailand"
replace delta=0.16 if country=="Colombia"
replace delta=0.28 if country=="Panama"
replace delta=0.29 if country=="Yugoslavia"
replace delta=0.14 if country=="Portugal"
replace delta=0.11 if country=="Uruguay"
replace delta=0.45 if country=="Greece"
replace delta=0.55 if country=="Ireland"
replace delta=0.42 if country=="Spain"
replace delta=0.49 if country=="Israel"
replace delta=0.40 if country=="Hong Kong"
replace delta=0.38 if country=="New Zealand"
replace delta=0.60 if country=="Austria"
replace delta=0.48 if country=="Singapore"
replace delta=0.60 if country=="Italy"
replace delta=0.58 if country=="UK"
replace delta=0.70 if country=="Japan"
replace delta=0.65 if country=="Belgium"
replace delta=0.47 if country=="Trinidad"
replace delta=0.72 if country=="Netherlands"
replace delta=0.65 if country=="Finland"
replace delta=0.73 if country=="Denmark"
replace delta=0.78 if country=="West Germany"
replace delta=0.74 if country=="France"
replace delta=0.57 if country=="Sweden"
replace delta=0.69 if country=="Norway"
replace delta=0.79 if country=="Switzerland"
replace delta=0.55 if country=="Canada"
replace delta=1 if country=="USA"

compress

label var country "Name of the country"
label var factor "Name of the factor"
label var AT "Factor content of trade F=A*T"
label var V "Endowment"
label var Y "GDP, World Bank, y=p*Q"
label var B "Trade balance, World Bank b=p*T"
label var YPC "GDP per capita, PWT"
label var indexc "Country indentifier"
label var indexf "Factor Indentifier"

* save c:\Empirical_Exercise\Chapter_2\trefler,replace *
save "Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-2\trefler", replace

exit
```

### My code

```{r ch2_ex0}
# Packages ----

library(archive)
library(readr)
library(dplyr)
library(tidyr)
library(purrr)
library(knitr)

# Extract ----

fzip <- "first-edition/Chapter-2.zip"
dout <- gsub("\\.zip$", "", fzip)

if (!dir.exists(dout)) {
  archive_extract(fzip, dir = dout)
}

# Read ----

fout <- paste0(dout, "/trefler.rds")
fout2 <- paste0(dout, "/trefler_desc.rds")

if (!file.exists(fout)) {
  trefler <- read_csv("first-edition/Chapter-2/hov_pub.csv", col_names = F) %>%
    rename(
      country = X1,
      factor = X2,
      at = X3,
      v = X4,
      y = X5,
      b = X6,
      ypc = X7,
      pop = X8
    )

  # Transform ----

  # see https://www.stata.com/manuals/rsummarize.pdf
  # https://www.stata.com/manuals/degen.pdf
  # https://www.stata.com/manuals/degen.pdf

  # Create an auxiliary table for delta values
  delta_values <- tibble(
    country = c(
      "Bangladesh", "Pakistan", "Indonesia", "Sri Lanka", "Thailand",
      "Colombia", "Panama", "Yugoslavia", "Portugal", "Uruguay", "Greece",
      "Ireland", "Spain", "Israel", "Hong Kong", "New Zealand", "Austria",
      "Singapore", "Italy", "UK", "Japan", "Belgium", "Trinidad", "Netherlands",
      "Finland", "Denmark", "West Germany", "France", "Sweden", "Norway",
      "Switzerland", "Canada", "USA"
    ),
    delta = c(
      0.03, 0.09, 0.10, 0.09, 0.17, 0.16, 0.28, 0.29, 0.14, 0.11, 0.45,
      0.55, 0.42, 0.49, 0.40, 0.38, 0.60, 0.48, 0.60, 0.58, 0.70, 0.65, 0.47,
      0.72, 0.65, 0.73, 0.78, 0.74, 0.57, 0.69, 0.79, 0.55, 1
    )
  )

  trefler <- trefler %>%
    mutate(ypc_max = max(ypc)) %>%
    mutate(
      ratio = case_when(
        country != "Italy" ~ ypc / ypc_max,
        country == "Italy" ~ (ypc / ypc_max) + 0.0001
      )
    ) %>%
    select(-ypc_max) %>%
    arrange(ratio) %>%
    group_by(ratio) %>%
    mutate(indexc = cur_group_id()) %>%
    group_by(factor) %>%
    mutate(indexf = cur_group_id()) %>%
    ungroup() %>%
    left_join(delta_values)

  # Labels ----

  # Create a separate table with the variables description

  trefler_desc <- tibble(
    variable = c(
      "country", "factor", "at", "v", "y", "b", "ypc", "indexc",
      "indexf"
    ),
    description = c(
      "Name of the country", "Name of the factor",
      "Factor content of trade F=A*T", "Endowment", "GDP, World Bank, y=p*Q",
      "Trade balance, World Bank b=p*T", "GDP per capita, PWT",
      "Country indentifier", "Factor Indentifier"
    )
  )

  # Save ----

  saveRDS(trefler, fout)
  saveRDS(trefler_desc, fout2)
} else {
  trefler <- readRDS(fout)
  trefler_desc <- readRDS(fout2)
}
```

## Exercise 1  

Given identical technologies across countries, run the program `sign_rank_1.do` to conduct the sign test, rank test, and test for missing trade. Use the results in `sign_rank_1.log` to replicate columns (2) and (4) in Table 2.5.

### Feenstra's code

```stata
* This program is to conduct sign test, Rank test and Missing trade test *

capture log close
* log using c:\Empirical_Exercise\Chapter_2\sign_rank_1.log, replace *
log using "Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-2\sign_rank_1.log", replace

set mem 30m

* use C:\Empirical_Exercise\Chapter_2\trefler, clear *
use "Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-2\trefler", clear

* number of country in the dataset *
egen C=max(indexc)
egen F=max(indexf)

* Calculate the world level of Yw, Bw and Vw *
egen Yww=sum(Y)
gen Yw=Yww/F
egen Bww=sum(B)
gen Bw=Bww/F
egen Vfw=sum(V), by(indexf)

* Calculate country share Sc *
gen Sc=(Y-B)/(Yw-Bw)

* Calculate epsilon(fc) and sigma^2(f) according to eq.2 in Trefler (1995)*
gen Efc=AT-(V-Sc*Vfw)

* Construct the average epsilon for a given factor *
egen total=sum(Efc),by(indexf)
gen ave=total/C

* Construct sigma^2 and the weight *

egen tot=sum((Efc-ave)^2), by(indexf)
gen sigma2f=tot/(C-1)

codebook sigma2f
gen sigmaf=sqrt(sigma2f)
gen weight=sigmaf*sqrt(Sc)

* Using the weight, convert all the data *

gen trAT=AT/(sigmaf*sqrt(Sc))
gen trV=V/(sigmaf*sqrt(Sc))
gen trY=Y/sqrt(Sc)
gen trB=B/sqrt(Sc)
gen trVfw=Vfw/sigmaf

gen AThat=trV-Sc*trVfw
gen AThat2=(V-Sc*Vfw)/weight

* Correlation, should be .28 *

corr trAT AThat2

*************
* Sign Test *
*************

sort indexc
by indexc: count if trAT*AThat2>0

count if trAT*AThat2>0
display _result(1)/_N

*****************
* Missing Trade *
*****************

* Checking for the missing trade, should be .032 *

quietly summarize trAT
local varAT=_result(4)
quietly summarize AThat
local varHat=_result(4)
quietly summarize AThat2
local varHat2=_result(4)
display `varAT'/`varHat'
display `varAT'/`varHat2'

**************
* Rank Tests *
**************

keep country indexc indexf trAT AThat2

sort indexc indexf
reshape wide trAT AThat2, i(indexc) j(indexf)

local i=1
while `i'<9{
	local j=`i'+1
	while `j'<=9{
		gen rank`i'`j'=((trAT`i'-trAT`j')*(AThat2`i'-AThat2`j')>0)
		local j=`j'+1
	}
	local i=`i'+1
}

keep country indexc rank*
reshape long rank, i(indexc) j(factor)
egen r1=sum(rank), by(indexc)
gen r2=r1/36
collapse r2,by(indexc country)
sum r2
list

log close
exit
```

### My code

```{r ch2_ex1_1}
# Transform ----

trefler <- readRDS(fout) %>%
  # Number of country in the dataset
  mutate(
    c = max(indexc),
    f = max(indexf)
  ) %>%
  # Calculate the world level of Yw, Bw and Vw
  mutate(
    yww = sum(y),
    yw = yww / f,
    bww = sum(b),
    bw = bww / f
  ) %>%
  group_by(indexf) %>%
  mutate(
    vfw = sum(v)
  ) %>%
  ungroup() %>%
  # Calculate country share Sc
  mutate(
    sc = (y - b) / (yw - bw)
  ) %>%
  # Calculate epsilon(fc) and sigma^2(f) according to eq.2 in Trefler (1995)
  mutate(
    efc = at - (v - sc * vfw)
  ) %>%
  # Construct the average epsilon for a given factor
  group_by(indexf) %>%
  mutate(ave = sum(efc) / c) %>%
  # Construct sigma^2 and the weight
  mutate(
    sigma2f = sum((efc - ave)^2) / (c - 1),
    sigmaf = sqrt(sigma2f),
    weight = sigmaf * sqrt(sc)
  ) %>%
  ungroup() %>%
  # Using the weight, convert all the data
  mutate(
    trat = at / (sigmaf * sqrt(sc)),
    athat2 = (v - (sc * vfw)) / weight
  ) %>%
  arrange(country)

# Correlation, should be .28
trefler %>%
  select(trat, athat2) %>%
  cor()

# Sign Test ----

trefler %>%
  group_by(country, indexc) %>%
  summarize(
    p = sum(trat * athat2 > 0) / n()
  )

trefler %>%
  summarize(
    p = sum(trat * athat2 > 0) / n()
  )

# Missing Trade ----

# Checking for the missing trade, should be .032

trefler %>%
  summarize(
    varat = var(trat),
    varhat2 = var(athat2)
  ) %>%
  mutate(
    varat_varhat2 = varat / varhat2
  )

# Rank Tests ----

trefler_wide <- trefler %>%
  select(country, indexc, indexf, trat, athat2) %>%
  arrange(indexc, indexf) %>%
  pivot_wider(
    names_from = indexf,
    values_from = c(trat, athat2)
  )

# This would be too long
# trefler_wide <- trefler_wide %>%
#   mutate(
#     rank12 = (trat_1 - trat_2) * (athat2_1 - athat2_2) > 0,
#     rank13 = (trat_1 - trat_3) * (athat2_1 - athat2_3) > 0,
#     ...
#     rank89 = (trat_8 - trat_9) * (athat2_8 - athat2_9) > 0,
#   )

# create all relevant trat_1 - trat_2, trat_1 - trat_3, etc.

ranks <- expand_grid(
  x = 1:8,
  y = 1:9
) %>%
  filter(x < y)

# The syntax here is based on internal R developer functions, but these
# allow to create columns with minimal lines of code and avoids more complicated
# bracket syntax
trefler_rank <- map2_df(
  pull(ranks, x),
  pull(ranks, y),
  function(x, y) {
    trefler_wide %>%
      mutate(
        name = paste0("rank", x, y),
        value = (!!sym(paste0("trat_", x)) - !!sym(paste0("trat_", y))) *
          (!!sym(paste0("athat2_", x)) - !!sym(paste0("athat2_", y))) > 0
      ) %>%
      select(country, indexc, name, value)
  }
) %>%
  group_by(country, indexc) %>%
  summarise(r1 = sum(value)) %>%
  mutate(r2 = r1 / 36)

trefler_rank

trefler_rank %>%
  pull(r2) %>%
  mean()
```

### Extra step: formatting the table

```{r ch2_ex1_2}
trefler %>%
  group_by(country, indexc) %>%
  summarize(
    p = sum(trat * athat2 > 0) / n()
  ) %>%
  arrange(indexc) %>% # same order as in the book
  select(country, sign_hov = p) %>%
  left_join(
    trefler_rank %>%
      select(country, rank_hov = r2)
  ) %>%
  bind_rows(
    trefler %>%
      summarize(
        p = sum(trat * athat2 > 0) / n()
      ) %>%
      mutate(
        country = "All countries",
        rank_hov = mean(pull(trefler_rank, r2))
      ) %>%
      select(country, sign_hov = p, rank_hov)
  ) %>%
  mutate_if(is.numeric, round, 2) %>% # same no of decimals as in the book
  kable()
```

## Exercise 2

Given uniform technological differences across countries, run the program `sign_rank_2.do` to redo the sign test, rank test, and missing trade.  Use the results in `sign_rank_2.log` to replicate column (3) and (5), given column (6) in Table 2.5.

### Feenstra's code

```stata
* This program is to conduct sign test, Rank test and Missing trade test *
* using delta *

capture log close
* log using c:\Empirical_Exercise\Chapter_2\sign_rank_2.log, replace *
log using "Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-2\sign_rank_2.log", replace

set mem 30m

* use c:\Empirical_Exercise\Chapter_2\trefler, clear *
use "Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-2\trefler", clear

* number of country in the dataset *
egen C=max(indexc)
egen F=max(indexf)

* Calculate the world level of Yw, Bw and Vw *
egen Yww=sum(Y)
gen Yw=Yww/F
egen Bww=sum(B)
gen Bw=Bww/F
egen Vfw=sum(V), by(indexf)
egen Vw=sum(delta*V), by(indexf)

* Calculate country share Sc *
gen Sc=(Y-B)/(Yw-Bw)

* Calculate epsilon(fc) and sigma^2(f) according to eq.2 in Trefler (1995)

gen Efc=delta*AT-(delta*V-Sc*Vw)

* Construct the average epsilon for a given factor *
egen total=sum(Efc),by(indexf)
gen ave=total/C

* Construct sigma^2 and the weight *

egen tot=sum((Efc-ave)^2), by(indexf)
gen sigma2f=tot/(C-1)

codebook sigma2f
gen sigmaf=sqrt(sigma2f)
gen weight=sigmaf*sqrt(Sc)

* Using the weight, convert all the data *

gen trAT=delta*AT/weight
gen AThat2=(delta*V-Sc*Vw)/weight

* Correlation *

corr trAT AThat2

*************
* Sign Test *
*************

sort indexc
by indexc: count if trAT*AThat2>0

count if trAT*AThat2>0
display _result(1)/_N

*****************
* Missing Trade *
*****************

quietly summarize trAT
local varAT=_result(4)
quietly summarize AThat
local varHat=_result(4)
quietly summarize AThat2
local varHat2=_result(4)
display `varAT'/`varHat'
display `varAT'/`varHat2'

*************
* Rank Test *
*************

keep country indexc indexf trAT AThat2

sort indexc indexf
reshape wide trAT AThat2, i(indexc) j(indexf)

local i=1
while `i'<9{
	local j=`i'+1
	while `j'<=9{
		gen rank`i'`j'=((trAT`i'-trAT`j')*(AThat2`i'-AThat2`j')>0)
		local j=`j'+1
	}
	local i=`i'+1
}

keep country indexc rank*
reshape long rank, i(indexc) j(factor)
egen r1=sum(rank), by(indexc)
gen r2=r1/36
collapse r2,by(indexc country)
sum r2
list

log close
exit
```

### My code

```{r ch2_ex2_1}
# Transform ----

trefler <- readRDS(fout) %>%
  # Number of country in the dataset
  mutate(
    c = max(indexc),
    f = max(indexf)
  ) %>%
  # Calculate the world level of Yw, Bw and Vw
  mutate(
    yww = sum(y),
    yw = yww / f,
    bww = sum(b),
    bw = bww / f
  ) %>%
  group_by(indexf) %>%
  mutate(
    vfw = sum(v),
    vw = sum(delta * v)
  ) %>%
  ungroup() %>%
  # Calculate country share Sc
  mutate(
    sc = (y - b) / (yw - bw)
  ) %>%
  # Calculate epsilon(fc) and sigma^2(f) according to eq.2 in Trefler (1995)
  mutate(
    efc = delta * at - (delta * v - sc * vw)
  ) %>%
  # Construct the average epsilon for a given factor
  group_by(indexf) %>%
  mutate(ave = sum(efc) / c) %>%
  # Construct sigma^2 and the weight
  mutate(
    sigma2f = sum((efc - ave)^2) / (c - 1),
    sigmaf = sqrt(sigma2f),
    weight = sigmaf * sqrt(sc)
  ) %>%
  ungroup() %>%
  # Using the weight, convert all the data
  mutate(
    trat = delta * at / weight,
    athat2 = (delta * v - (sc * vw)) / weight
  )

# Correlation should be .41
trefler %>%
  select(trat, athat2) %>%
  cor()

# Sign Test ----

trefler %>%
  group_by(country, indexc) %>%
  summarize(
    p = sum(trat * athat2 > 0) / n()
  )

trefler %>%
  summarize(
    p = sum(trat * athat2 > 0) / n()
  )

# Missing Trade ----

# Checking for the missing trade, should be .07

trefler %>%
  summarize(
    varat = var(trat),
    varhat2 = var(athat2)
  ) %>%
  mutate(
    varat_varhat2 = varat / varhat2
  )

# Rank Tests ----

trefler_wide <- trefler %>%
  select(country, indexc, indexf, trat, athat2) %>%
  arrange(indexc, indexf) %>%
  pivot_wider(
    names_from = indexf,
    values_from = c(trat, athat2)
  )

ranks <- expand_grid(
  x = 1:8,
  y = 1:9
) %>%
  filter(x < y)

trefler_rank <- map2_df(
  pull(ranks, x),
  pull(ranks, y),
  function(x, y) {
    trefler_wide %>%
      mutate(
        name = paste0("rank", x, y),
        value = (!!sym(paste0("trat_", x)) - !!sym(paste0("trat_", y))) *
          (!!sym(paste0("athat2_", x)) - !!sym(paste0("athat2_", y))) > 0
      ) %>%
      select(country, indexc, name, value)
  }
) %>%
  group_by(country, indexc) %>%
  summarise(r1 = sum(value)) %>%
  mutate(r2 = r1 / 36)

trefler_rank

trefler_rank %>%
  pull(r2) %>%
  mean()
```

### Extra step: formatting the table

```{r ch2_ex2_2}
trefler %>%
  group_by(country, indexc) %>%
  summarize(
    p = sum(trat * athat2 > 0) / n()
  ) %>%
  arrange(indexc) %>% # same order as in the book
  select(country, sign_hov = p) %>%
  left_join(
    trefler_rank %>%
      select(country, rank_hov = r2)
  ) %>%
  bind_rows(
    trefler %>%
      summarize(
        p = sum(trat * athat2 > 0) / n()
      ) %>%
      mutate(
        country = "All countries",
        rank_hov = mean(pull(trefler_rank, r2))
      ) %>%
      select(country, sign_hov = p, rank_hov)
  ) %>%
  mutate_if(is.numeric, round, 2) %>% # same no of decimals as in the book
  kable()
```

### Notes

The Stata code that I run returns the same values as R. However:

* Austria should have values 0.67 and 0.47. I got 0.67 and 0.44.
* France should have values 0.33 and 0.22. I got 0.33 and 0.19.
* Switzerland should have values 0.89 and 0.47. I got 0.89 and 0.50.

## Exercise 3

Allowing all factors in each country to have different productivities, now run the program `compute_pi.do` to compute factor productivities $\pi_k^i$ as Trefler (1993).  Note that there are 9 factors in the original data set, but these are now aggregated to just 4 factors, which are labor (endowment 1), capital (endowment 2), cropland (endowment 3) and pasture (endowment 4).  Using the results in `pi_.log` or alternatively in the data files `pi_1.dta, pi_2.dta, pi_3.dta, pi_4.dta` to answer the following:

(a)  Which factor has the most negative productivities estimated?
(b)  What is the correlation between the estimated labor productivity and the productivities of other factors?  What is the correlation between each factor productivity and GDP per-capita (which you can find in the file `trefler.dta`)?

### Feenstra's code

```stata
* This program is to compute pai, the factor productivity *

capture log close
* log using c:\Empirical_Exercise\Chapter_2\pi.log,replace *
log using "Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-2\pi.log", replace

set mem 30m

* use c:\Empirical_Exercise\Chapter_2\trefler, clear *
use "Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-2\trefler", clear

* number of country in the dataset *
egen C=max(indexc)
egen F=max(indexf)

* Calculate the world level of Yw, Bw and Vw *
egen Yww=sum(Y)
gen Yw=Yww/F
egen Bww=sum(B)
gen Bw=Bww/F
egen Vfw=sum(V), by(indexf)

* Calculate country share Sc *
gen Sc=(Y-B)/(Yw-Bw)

* Calculate epsilon(fc) and sigma^2(f) according to eq.2 in Trefler (1995)
gen Efc=AT-(V-Sc*Vfw)

* Construct the average epsilon for a given factor *
egen total=sum(Efc),by(indexf)
gen ave=total/C

* Construct sigma^2 and the weight *

egen tot=sum((Efc-ave)^2), by(indexf)
gen sigma2f=tot/(C-1)

codebook sigma2f
gen sigmaf=sqrt(sigma2f)
gen weight=sigmaf*sqrt(Sc)

* Using the weight, convert all the data *

gen trAT=AT/(sigmaf*sqrt(Sc))
gen trV=V/(sigmaf*sqrt(Sc))
gen trY=Y/sqrt(Sc)
gen trB=B/sqrt(Sc)
gen trVfw=Vfw/sigmaf

gen AThat=trV-Sc*trVfw
gen AThat2=(V-Sc*Vfw)/weight

* Construct Aggregate Labor Endowment *

preserve
keep if indexf==7 |indexf==8 | indexf==9
gen en=2
replace en=3 if indexf==8
replace en=4 if indexf==9
keep country factor AT V en indexc Sc

* save c:\Empirical_Exercise\Chapter_2\indexf_189,replace *
save "Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-2\indexf_189", replace

restore

preserve
drop if indexf==7 |indexf==8 | indexf==9

egen v_l=sum(V), by(country)
egen AT_l=sum(AT), by(country)

drop V AT factor
rename v_l V
rename AT_l AT
gen en=1
collapse (mean)AT V en indexc Sc, by(country)
gen str5 factor="Labor"
* save c:\Empirical_Exercise\Chapter_2\indexf_L,replace *
save "Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-2\indexf_L", replace

restore

* use c:\Empirical_Exercise\Chapter_2\indexf_189,clear *
use "Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-2\indexf_189", clear

* append using c:\Empirical_Exercise\Chapter_2\indexf_L *
append using "Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-2\indexf_L"
sort indexc en
* save c:\Empirical_Exercise\Chapter_2\pi,replace *
save "Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-2\pi", replace

************************************
* Compute Pi: factor productivity *
************************************

* use c:\Empirical_Exercise\Chapter_2\pi, clear *
use "Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-2\pi", clear

gen p_0=1
gen p_1=1

local i=1
while `i'<=4{
	preserve
	keep if en==`i'
	local j=1
	while `j'<51{
		replace p_0=p_1
		gen Vp=p_0*V
		egen Vpw=sum(Vp)
		replace p_1=(AT+Sc*Vpw)/V
		replace p_1=1 if country=="USA"
		drop Vp Vpw
		local j=`j'+1
	}
	keep en country indexc p_1
	* save c:\Empirical_Exercise\Chapter_2\pi_`i',replace *
  save "Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-2\pi_`i'", replace
	restore
	local i=`i'+1
}

local i=1
while `i'<=4{
	* use c:\Empirical_Exercise\Chapter_2\pi_`i',clear *
  use "Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-2\pi_`i'", clear
	sort en indexc
	by en: list en indexc country p_1
	local i=`i'+1
}

log close

exit
```

### My code

```{r ch2_ex3}
trefler <- readRDS(fout) %>%
  # Number of country in the dataset
  mutate(
    c = max(indexc),
    f = max(indexf)
  ) %>%
  # Calculate the world level of Yw, Bw and Vw
  mutate(
    yww = sum(y),
    yw = yww / f,
    bww = sum(b),
    bw = bww / f
  ) %>%
  group_by(indexf) %>%
  mutate(
    vfw = sum(v),
    vw = sum(delta * v)
  ) %>%
  ungroup() %>%
  # Calculate country share Sc
  mutate(
    sc = (y - b) / (yw - bw)
  ) %>%
  # Calculate epsilon(fc) and sigma^2(f) according to eq.2 in Trefler (1995)
  mutate(
    efc = delta * at - (delta * v - sc * vw)
  ) %>%
  # Construct the average epsilon for a given factor
  group_by(indexf) %>%
  mutate(ave = sum(efc) / c) %>%
  # Construct sigma^2 and the weight
  mutate(
    sigma2f = sum((efc - ave)^2) / (c - 1),
    sigmaf = sqrt(sigma2f),
    weight = sigmaf * sqrt(sc)
  ) %>%
  ungroup() %>%
  # Using the weight, convert all the data
  mutate(
    trat = delta * at / weight,
    athat2 = (delta * v - (sc * vw)) / weight
  )

# No need to save changes and restore
trefler2 <- trefler %>%
  # Construct Aggregate Labor Endowment
  filter(indexf %in% 7:9) %>%
  mutate(
    en = case_when(
      indexf == 7 ~ 2,
      indexf == 8 ~ 3,
      indexf == 9 ~ 4
    )
  ) %>%
  select(country, factor, indexf, at, v, en, indexc, sc)

trefler3 <- trefler %>%
  filter(!(indexf %in% 7:9)) %>%
  group_by(country) %>%
  # No need to create v_l and at_l to then rename and then collapse
  summarise(
    v = sum(v),
    at = sum(at),
    sc = mean(sc),
    indexc = mean(indexc)
  ) %>%
  mutate(
    en = 1,
    factor = "Labor"
  )

trefler3 <- trefler2 %>%
  select(-indexf) %>%
  bind_rows(trefler3) %>%
  arrange(indexc, en)

# Compute Pi: factor productivity
# No need to save intermediate outputs, we proceed with iteration
trefler4 <- map_df(
  trefler3 %>%
    distinct(en) %>%
    pull(),
  function(x) {
    d <- trefler3 %>%
      filter(en == x) %>%
      mutate(p0 = 1, p1 = 1)

    iter <- 50

    for (i in seq_len(iter)) {
      d <- d %>%
        mutate(
          p0 = p1,
          vp = p0 * v,
          vpw = sum(vp),
          p1 = ifelse(country == "USA", 1, (at + sc * vpw) / v)
        ) %>%
        select(-vp, -vpw)
    }

    # Tidy alternative to the for loop
    # d <- accumulate(seq_len(iter), .init = d, ~ .x %>%
    #   mutate(
    #     p0 = p1,
    #     p1 = ifelse(country == "USA", 1, (at + sc * sum(p1 * v)) / v)
    #   )) %>%
    #   .[[iter + 1]]

    d %>%
      select(country, indexc, en, p1)
  }
)
```

### Extra step: formatting the tables

```{r ch2_ex3_2}
trefler4 %>%
  arrange(country, en) %>%
  kable()
```
