
# Chapter 5. Increasing Returns and the Gravity Equation

## Empirical exercise

In this exercise, you are asked to reproduce the empirical results shown in Table 5.2. There are  four datasets available: `dist.csv` which is distances; `gdp_ce_93.csv` which is GDP in exporting location in 1993; `gdp_ci_93.csv` which is GDP in importing location in 1993; and `trade_93.csv` which is trade in 1993. To complete the exercise, these files should be stored in the directory `Chapter-5`. After this, run the STATA program `data_trans.do`, which will convert these datasets to STATA files with the same name. The trade data is already converted into US dollars, but GDP data is in Canadian dollars, so this is converted with the exchange rate 1 Canadian dollar = 0.775134 U.S. dollars.

## Documentation

US-Canada data for Anderson and van Wincoop (2002) 

There are a total of 63 US-Canada regions (states, District of Columbia, provinces and territories). They are listed below. The regressions, however, are based on the same 40 states and provinces as in McCallum (these are indicated with a star below). 

| Code | State/Province         |
|------|------------------------|
| 1    | Alabama*               |
| 2    | Alaska                 |
| 3    | Arizona*               |
| 4    | Arkansas               |
| 5    | California*            |
| 6    | Colorado               |
| 7    | Connecticut            |
| 8    | Delaware               |
| 9    | Florida*               |
| 10   | Georgia*               |
| 11   | Hawaii                 |
| 12   | Idaho*                 |
| 13   | Illinois*              |
| 14   | Indiana*               |
| 15   | Iowa                   |
| 16   | Kansas                 |
| 17   | Kentucky*              |
| 18   | Louisiana*             |
| 19   | Maine*                 |
| 20   | Maryland*              |
| 21   | Massachusetts*         |
| 22   | Michigan*              |
| 23   | Minnesota*             |
| 24   | Mississippi            |
| 25   | Missouri*              |
| 26   | Montana*               |
| 27   | Nebraska               |
| 28   | Nevada                 |
| 29   | New Hampshire*         |
| 30   | New Jersey*            |
| 31   | New Mexico             |
| 32   | New York*              |
| 33   | North Carolina*        |
| 34   | North Dakota*          |
| 35   | Ohio*                  |
| 36   | Oklahoma               |
| 37   | Oregon                 |
| 38   | Pennsylvania*          |
| 39   | Rhode Island           |
| 40   | South Carolina         |
| 41   | South Dakota           |
| 42   | Tennessee*             |
| 43   | Texas*                 |
| 44   | Utah                   |
| 45   | Vermont*               |
| 46   | Virginia*              |
| 47   | Washington*            |
| 48   | West Virginia          |
| 49   | Wisconsin*             |
| 50   | Wyoming                |
| 51   | Dist. of Col.          |
| 52   | Alberta*               |
| 53   | British Columbia*      |
| 54   | Manitoba*              |
| 55   | New Brunswick*         |
| 56   | Newfoundland*          |
| 57   | NW Territories         |
| 58   | Nova Scotia*           |
| 59   | Ontario*               |
| 60   | Prince Edward Island*  |
| 61   | Quebec*                |
| 62   | Saskatchewan*          |
| 63   | Yukon Territory        |

Data files:

1. dist.csv: Contains distances between the 40 regions listed above. The distances are in kilometers and are between the capitals of the regions. 
2. gdp_ce_93.csv and gdp_ci_93.csv: Contains nominal GDP in millions of Canadian dollars in 1993 for the 40 regions above. 
3. trade_93.csv

Contains 1993 trade data between the 40 regions listed above, in US dollars. The indicator variables `1_ex` and `1_im` equal 1 if the exporter or importer is a US state, and 2 for a Canadian province.

## Exercise 1

Run the program `gravity_1.do` to replicate the gravity equations in columns (1)-(3) of Table 5.2.

### Feenstra's code

Data transformation:

```stata
* Input data set into STATA and save as STATA file *

insheet using Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-5\dist.csv
sort c_e c_i
save Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-5\dist,replace

clear
insheet using Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-5\trade_93.csv
sort c_e c_i

merge c_e c_i using Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-5\dist
drop _merge

sort c_e c_i

save Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-5\trade_93,replace

clear

insheet using Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-5\gdp_ce_93.csv
gen gce=gdp_ce*0.775134
drop gdp_ce
ren gce gdp_ce
sort c_e
save Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-5\gdp_ce_93,replace

clear

insheet using Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-5\gdp_ci_93.csv
gen gci=gdp_ci*0.775134
drop gdp_ci
ren gci gdp_ci
sort c_i
save Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-5\gdp_ci_93,replace

clear
```

Models:

```stata
capture log close
log using Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-5\gravity_1.log, replace

set matsize 100

use Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-5\trade_93,clear
sort c_e
merge c_e using Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-5\gdp_ce_93
drop _merge
sort c_i
merge c_i using Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-5\gdp_ci_93
drop _merge
drop if vx==0
drop if dist==0

gen lnvx=log(vx)
gen lndist=log(dist)
gen lngdp_ce=log(gdp_ce)
gen lngdp_ci=log(gdp_ci)

* Estimate Gravity Equation from the Canadian Perspective *

preserve
gen d_ca=0
replace d_ca=1 if (l_ex==2) & (l_im==2)
drop if (l_ex==1) & (l_im==1)

regress lnvx lngdp_ce lngdp_ci lndist d_ca
restore

* Estimate Gravity Equation from the U.S. Perspective *

preserve
gen d_us=0
replace d_us=1 if (l_ex==1) & (l_im==1)
drop if (l_ex==2) & (l_im==2)

regress lnvx lngdp_ce lngdp_ci lndist d_us
restore

* Estimate Gravity Equation by Pooling All Data *

preserve
gen d_ca=0
gen d_us=0
replace d_ca=1 if (l_ex==2) & (l_im==2)
replace d_us=1 if (l_ex==1) & (l_im==1)

regress lnvx lngdp_ce lngdp_ci lndist d_ca d_us
vce
restore

clear

log close
```

Output:

```stata
. capture log close

. log using Z:\home\pacha\github\advanced-international-trade\first-edition\Chapte
> r-5\gravity_1.log, replace
(note: file Z:\home\pacha\github\advanced-international-trade\first-edition\Chapte
> r-5\gravity_1.log not found)
----------------------------------------------------------------------------------
      name:  <unnamed>
       log:  Z:\home\pacha\github\advanced-international-trade\first-edition\Chapt
> er-5\gravity_1.log
  log type:  text
 opened on:  19 Jun 2024, 13:34:35

. 
. set matsize 100

Current memory allocation

                    current                                 memory usage
    settable          value     description                 (1M = 1024k)
    --------------------------------------------------------------------
    set maxvar         5000     max. variables allowed           1.909M
    set memory           50M    max. data space                 50.000M
    set matsize         100     max. RHS vars in models          0.085M
                                                            -----------
                                                                51.994M

. 
. use Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-5\tr
> ade_93,clear

. sort c_e

. merge c_e using Z:\home\pacha\github\advanced-international-trade\first-edition\
> Chapter-5\gdp_ce_93
(note: you are using old merge syntax; see [R] merge for new syntax)
variable c_e does not uniquely identify observations in the master data

. drop _merge

. sort c_i

. merge c_i using Z:\home\pacha\github\advanced-international-trade\first-edition\
> Chapter-5\gdp_ci_93
(note: you are using old merge syntax; see [R] merge for new syntax)
variable c_i does not uniquely identify observations in the master data

. drop _merge

. drop if vx==0
(49 observations deleted)

. drop if dist==0
(40 observations deleted)

. 
. gen lnvx=log(vx)

. gen lndist=log(dist)

. gen lngdp_ce=log(gdp_ce)

. gen lngdp_ci=log(gdp_ci)

. 
. * Estimate Gravity Equation from the Canadian Perspective *
. 
. preserve

. gen d_ca=0

. replace d_ca=1 if (l_ex==2) & (l_im==2)
(90 real changes made)

. drop if (l_ex==1) & (l_im==1)
(832 observations deleted)

. 
. regress lnvx lngdp_ce lngdp_ci lndist d_ca

      Source |       SS       df       MS              Number of obs =     679
-------------+------------------------------           F(  4,   674) =  540.02
       Model |  3020.52204     4  755.130511           Prob > F      =  0.0000
    Residual |  942.471913   674  1.39832628           R-squared     =  0.7622
-------------+------------------------------           Adj R-squared =  0.7608
       Total |  3962.99396   678  5.84512383           Root MSE      =  1.1825

------------------------------------------------------------------------------
        lnvx |      Coef.   Std. Err.      t    P>|t|     [95% Conf. Interval]
-------------+----------------------------------------------------------------
    lngdp_ce |   1.218705   .0331581    36.75   0.000       1.1536    1.283811
    lngdp_ci |   .9797792   .0325254    30.12   0.000     .9159159    1.043642
      lndist |  -1.353149   .0690128   -19.61   0.000    -1.488655   -1.217643
        d_ca |   2.802034   .1416955    19.78   0.000     2.523816    3.080251
       _cons |   3.742672   .7721966     4.85   0.000     2.226472    5.258873
------------------------------------------------------------------------------

. restore

. 
. * Estimate Gravity Equation from the U.S. Perspective *
. 
. preserve

. gen d_us=0

. replace d_us=1 if (l_ex==1) & (l_im==1)
(832 real changes made)

. drop if (l_ex==2) & (l_im==2)
(90 observations deleted)

. 
. regress lnvx lngdp_ce lngdp_ci lndist d_us

      Source |       SS       df       MS              Number of obs =    1421
-------------+------------------------------           F(  4,  1416) = 2052.61
       Model |  7089.25392     4  1772.31348           Prob > F      =  0.0000
    Residual |  1222.63635  1416  .863443752           R-squared     =  0.8529
-------------+------------------------------           Adj R-squared =  0.8525
       Total |  8311.89028  1420  5.85344386           Root MSE      =  .92922

------------------------------------------------------------------------------
        lnvx |      Coef.   Std. Err.      t    P>|t|     [95% Conf. Interval]
-------------+----------------------------------------------------------------
    lngdp_ce |   1.128429    .020453    55.17   0.000     1.088308     1.16855
    lngdp_ci |   .9820314    .020396    48.15   0.000     .9420218    1.022041
      lndist |  -1.081888    .035227   -30.71   0.000    -1.150991   -1.012785
        d_us |   .4059649   .0578667     7.02   0.000     .2924511    .5194786
       _cons |   2.659586   .4492747     5.92   0.000      1.77827    3.540901
------------------------------------------------------------------------------

. restore

. 
. * Estimate Gravity Equation by Pooling All Data *
. 
. preserve

. gen d_ca=0

. gen d_us=0

. replace d_ca=1 if (l_ex==2) & (l_im==2)
(90 real changes made)

. replace d_us=1 if (l_ex==1) & (l_im==1)
(832 real changes made)

. 
. regress lnvx lngdp_ce lngdp_ci lndist d_ca d_us

      Source |       SS       df       MS              Number of obs =    1511
-------------+------------------------------           F(  5,  1505) = 1732.75
       Model |  7499.70876     5  1499.94175           Prob > F      =  0.0000
    Residual |  1302.79013  1505  .865641282           R-squared     =  0.8520
-------------+------------------------------           Adj R-squared =  0.8515
       Total |  8802.49889  1510  5.82946946           Root MSE      =   .9304

------------------------------------------------------------------------------
        lnvx |      Coef.   Std. Err.      t    P>|t|     [95% Conf. Interval]
-------------+----------------------------------------------------------------
    lngdp_ce |   1.132974   .0196797    57.57   0.000     1.094371    1.171577
    lngdp_ci |   .9742161   .0196294    49.63   0.000     .9357122     1.01272
      lndist |  -1.110705   .0337347   -32.92   0.000    -1.176877   -1.044533
        d_ca |   2.751708   .1086755    25.32   0.000     2.538536    2.964879
        d_us |   .3982716   .0574423     6.93   0.000     .2855962    .5109471
       _cons |   2.911512   .4267171     6.82   0.000     2.074488    3.748535
------------------------------------------------------------------------------

. vce

Covariance matrix of coefficients of regress model

        e(V) |   lngdp_ce    lngdp_ci      lndist        d_ca        d_us 
-------------+------------------------------------------------------------
    lngdp_ce |  .00038729                                                 
    lngdp_ci |  .00008279   .00038531                                     
      lndist |  .00001868   .00001752   .00113803                         
        d_ca |  .00041241   .00040103   .00017043   .01181037             
        d_us | -.00037488  -.00039315   .00039698   .00085625   .00329962 
       _cons | -.00524428  -.00520461   -.0089485  -.01157481   .00387661 

        e(V) |      _cons 
-------------+------------
       _cons |  .18208752 

. restore

. 
. clear

. 
. log close
      name:  <unnamed>
       log:  Z:\home\pacha\github\advanced-international-trade\first-edition\Chapt
> er-5\gravity_1.log
  log type:  text
 closed on:  19 Jun 2024, 13:34:38
----------------------------------------------------------------------------------

. 
. 
. 
. 
end of do-file
```

### My code

```{r ch2_ex1}
# Packages ----

library(archive)
library(readr)
library(janitor)
library(dplyr)

# Extract ----

fzip <- "first-edition/Chapter-5.zip"
dout <- gsub("\\.zip$", "", fzip)

if (!dir.exists(dout)) {
  archive_extract(fzip, dir = dout)
}

# Read and transform ----

fout <- paste0(dout, "/trade_93.rds")

if (!file.exists(fout)) {
  # trade_93 <- read_dta(paste0(dout, "/trade_93.dta"))
  # gdp_ce_93 <- read_dta(paste0(dout, "/gdp_ce_93.dta"))
  # gdp_ci_93 <- read_dta(paste0(dout, "/gdp_ci_93.dta"))

  # instead of reading the DTA files, I will read the CSV files and transform

  dist <- read_csv(paste0(dout, "/dist.csv")) %>%
    clean_names() %>%
    arrange(c_e, c_i)

  trade_93 <- read_csv(paste0(dout, "/trade_93.csv")) %>%
    clean_names() %>%
    arrange(c_e, c_i)

  trade_93 <- trade_93 %>%
    left_join(dist, by = c("c_e", "c_i"))

  rm(dist)

  gdp_ce_93 <- read_csv(paste0(dout, "/gdp_ce_93.csv")) %>%
    clean_names() %>%
    mutate(gdp_ce = gdp_ce * 0.775134) %>%
    arrange(c_e)

  gdp_ci_93 <- read_csv(paste0(dout, "/gdp_ci_93.csv")) %>%
    clean_names() %>%
    mutate(gdp_ci = gdp_ci * 0.775134) %>%
    arrange(c_i)

  trade_93 <- trade_93 %>%
    left_join(gdp_ce_93, by = "c_e") %>%
    left_join(gdp_ci_93, by = "c_i") %>%
    filter(vx != 0, dist != 0) %>%
    mutate(
      lnvx = log(vx),
      lndist = log(dist),
      lngdp_ce = log(gdp_ce),
      lngdp_ci = log(gdp_ci)
    )

  saveRDS(trade_93, fout)
} else {
  trade_93 <- readRDS(fout)
}

# Estimate Gravity Equation from the Canadian Perspective ----

trade_93_2 <- trade_93 %>%
  mutate(d_ca = ifelse(l_ex == 2 & l_im == 2, 1, 0)) %>%
  filter(l_ex != 1 | l_im != 1)

fit_ca <- lm(lnvx ~ lngdp_ce + lngdp_ci + lndist + d_ca, data = trade_93_2)

summary(fit_ca)

# Estimate Gravity Equation from the U.S. Perspective ----

trade_93_3 <- trade_93 %>%
  mutate(d_us = ifelse(l_ex == 1 & l_im == 1, 1, 0)) %>%
  filter(l_ex != 2 | l_im != 2)

fit_us <- lm(lnvx ~ lngdp_ce + lngdp_ci + lndist + d_us, data = trade_93_3)

summary(fit_us)

# Estimate Gravity Equation by Pooling All Data ----

trade_93_4 <- trade_93 %>%
  mutate(
    d_ca = ifelse(l_ex == 2 & l_im == 2, 1, 0),
    d_us = ifelse(l_ex == 1 & l_im == 1, 1, 0)
  )

fit_all <- lm(
  lnvx ~ lngdp_ce + lngdp_ci + lndist + d_ca + d_us,
  data = trade_93_4
)

summary(fit_all)

vcov(fit_all)
```

## Exercise 2

Run the program `gravity_2.do` to replicate gravity equation using fixed-effects, i.e., column (5) in Table 5.2. Then answer:

a. How are these results affected if we allow the provincial and state GDP’s to have coefficients different from unity?
b. What coefficients are obtained if we introduce separate indicator variables for intra-Canadian and intra-U.S. trade, rather than the border dummy?

### Feenstra's code

```stata
capture log close
log using Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-5\gravity_2.log, replace

set matsize 100

use Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-5\trade_93,clear
sort c_e
merge c_e using Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-5\gdp_ce_93
drop _merge
sort c_i
merge c_i using Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-5\gdp_ci_93
drop _merge
drop if vx==0
drop if dist==0

tab c_e, gen (ced)
tab c_i, gen (cid)

gen d_border=1
replace d_border=0 if (l_ex==1) & (l_im==1)
replace d_border=0 if (l_ex==2) & (l_im==2)

gen lnvx=log(vx)
gen lndist=log(dist)
gen lngdp_ce=log(gdp_ce)
gen lngdp_ci=log(gdp_ci)
gen lnn_vx=lnvx-lngdp_ce-lngdp_ci

regress lnn_vx lndist d_border ced* cid*

clear
log close
```

Output:

```stata
. capture log close

. log using Z:\home\pacha\github\advanced-international-trade\first-edition\Chapte
> r-5\gravity_2.log, replace
(note: file Z:\home\pacha\github\advanced-international-trade\first-edition\Chapte
> r-5\gravity_2.log not found)
----------------------------------------------------------------------------------
      name:  <unnamed>
       log:  Z:\home\pacha\github\advanced-international-trade\first-edition\Chapt
> er-5\gravity_2.log
  log type:  text
 opened on:  19 Jun 2024, 13:41:01

. 
. set matsize 100

Current memory allocation

                    current                                 memory usage
    settable          value     description                 (1M = 1024k)
    --------------------------------------------------------------------
    set maxvar         5000     max. variables allowed           1.909M
    set memory           50M    max. data space                 50.000M
    set matsize         100     max. RHS vars in models          0.085M
                                                            -----------
                                                                51.994M

. 
. use Z:\home\pacha\github\advanced-international-trade\first-edition\Chapter-5\tr
> ade_93,clear

. sort c_e

. merge c_e using Z:\home\pacha\github\advanced-international-trade\first-edition\
> Chapter-5\gdp_ce_93
(note: you are using old merge syntax; see [R] merge for new syntax)
variable c_e does not uniquely identify observations in the master data

. drop _merge

. sort c_i

. merge c_i using Z:\home\pacha\github\advanced-international-trade\first-edition\
> Chapter-5\gdp_ci_93
(note: you are using old merge syntax; see [R] merge for new syntax)
variable c_i does not uniquely identify observations in the master data

. drop _merge

. drop if vx==0
(49 observations deleted)

. drop if dist==0
(40 observations deleted)

. 
. tab c_e, gen (ced)

        c_e |      Freq.     Percent        Cum.
------------+-----------------------------------
         AB |         39        2.58        2.58
        Ala |         38        2.51        5.10
        Ari |         37        2.45        7.54
         BC |         39        2.58       10.13
        Cal |         37        2.45       12.57
        Flo |         39        2.58       15.16
        Geo |         39        2.58       17.74
        Ida |         36        2.38       20.12
        Ill |         39        2.58       22.70
        Ind |         38        2.51       25.22
        Ken |         37        2.45       27.66
        Lou |         36        2.38       30.05
         MN |         39        2.58       32.63
         MO |         37        2.45       35.08
        Mai |         37        2.45       37.52
        Mas |         39        2.58       40.11
        Mic |         37        2.45       42.55
        Min |         38        2.51       45.07
        Mon |         36        2.38       47.45
        Mry |         37        2.45       49.90
         NB |         39        2.58       52.48
        NHm |         38        2.51       55.00
        NJr |         39        2.58       57.58
         NS |         39        2.58       60.16
        Nca |         39        2.58       62.74
        Nda |         36        2.38       65.12
       Nfld |         35        2.32       67.44
        Nyr |         39        2.58       70.02
         ON |         39        2.58       72.60
        Ohi |         37        2.45       75.05
        PEI |         34        2.25       77.30
        Pen |         39        2.58       79.88
        Que |         39        2.58       82.46
         SK |         39        2.58       85.04
        Ten |         38        2.51       87.56
        Tex |         37        2.45       90.01
        Ver |         37        2.45       92.46
        Vir |         39        2.58       95.04
        Was |         36        2.38       97.42
        Wis |         39        2.58      100.00
------------+-----------------------------------
      Total |      1,511      100.00

. tab c_i, gen (cid)

        c_I |      Freq.     Percent        Cum.
------------+-----------------------------------
         AB |         39        2.58        2.58
        Ala |         38        2.51        5.10
        Ari |         36        2.38        7.48
         BC |         39        2.58       10.06
        Cal |         39        2.58       12.64
        Flo |         39        2.58       15.22
        Geo |         39        2.58       17.80
        Ida |         33        2.18       19.99
        Ill |         39        2.58       22.57
        Ind |         39        2.58       25.15
        Ken |         37        2.45       27.60
        Lou |         36        2.38       29.98
         MN |         39        2.58       32.56
         MO |         39        2.58       35.14
        Mai |         36        2.38       37.52
        Mas |         37        2.45       39.97
        Mic |         39        2.58       42.55
        Min |         39        2.58       45.14
        Mon |         34        2.25       47.39
        Mry |         39        2.58       49.97
         NB |         39        2.58       52.55
        NHm |         38        2.51       55.06
        NJr |         39        2.58       57.64
         NS |         39        2.58       60.23
        Nca |         39        2.58       62.81
        Nda |         31        2.05       64.86
       Nfld |         38        2.51       67.37
        Nyr |         37        2.45       69.82
         ON |         39        2.58       72.40
        Ohi |         38        2.51       74.92
        PEI |         38        2.51       77.43
        Pen |         38        2.51       79.95
        Que |         39        2.58       82.53
         SK |         39        2.58       85.11
        Ten |         39        2.58       87.69
        Tex |         39        2.58       90.27
        Ver |         33        2.18       92.46
        Vir |         38        2.51       94.97
        Was |         37        2.45       97.42
        Wis |         39        2.58      100.00
------------+-----------------------------------
      Total |      1,511      100.00

. 
. gen d_border=1

. replace d_border=0 if (l_ex==1) & (l_im==1)
(832 real changes made)

. replace d_border=0 if (l_ex==2) & (l_im==2)
(90 real changes made)

. 
. gen lnvx=log(vx)

. gen lndist=log(dist)

. gen lngdp_ce=log(gdp_ce)

. gen lngdp_ci=log(gdp_ci)

. gen lnn_vx=lnvx-lngdp_ce-lngdp_ci

. 
. regress lnn_vx lndist d_border ced* cid*
note: ced39 omitted because of collinearity
note: cid37 omitted because of collinearity

      Source |       SS       df       MS              Number of obs =    1511
-------------+------------------------------           F( 80,  1430) =   35.32
       Model |  1998.34711    80  24.9793388           Prob > F      =  0.0000
    Residual |   1011.4731  1430  .707323845           R-squared     =  0.6639
-------------+------------------------------           Adj R-squared =  0.6451
       Total |   3009.8202  1510  1.99325841           Root MSE      =  .84103

------------------------------------------------------------------------------
      lnn_vx |      Coef.   Std. Err.      t    P>|t|     [95% Conf. Interval]
-------------+----------------------------------------------------------------
      lndist |  -1.251681   .0368191   -34.00   0.000    -1.323906   -1.179456
    d_border |  -1.550514   .0588941   -26.33   0.000    -1.666042   -1.434986
        ced1 |   1.575054   .1969728     8.00   0.000     1.188667    1.961441
        ced2 |  -.0615169   .1968394    -0.31   0.755    -.4476419    .3246082
        ced3 |  -.2180008   .1971536    -1.11   0.269     -.604742    .1687405
        ced4 |   1.373042   .1968679     6.97   0.000     .9868611    1.759223
        ced5 |   .3855025    .197204     1.95   0.051    -.0013377    .7723426
        ced6 |  -.7112586   .1952711    -3.64   0.000    -1.094307   -.3282102
        ced7 |   -.068018   .1960215    -0.35   0.729    -.4525384    .3165025
        ced8 |     .26858   .1986056     1.35   0.176    -.1210097    .6581697
        ced9 |   .2175036   .1965116     1.11   0.269    -.1679784    .6029856
       ced10 |  -.0031177   .1983064    -0.02   0.987    -.3921204    .3858849
       ced11 |   .1779582   .1996637     0.89   0.373     -.213707    .5696233
       ced12 |  -.2567707   .1990797    -1.29   0.197    -.6472903    .1337489
       ced13 |   1.044481   .1978236     5.28   0.000     .6564256    1.432537
       ced14 |   .1701477   .1984997     0.86   0.391    -.2192341    .5595295
       ced15 |  -.1910339   .1989122    -0.96   0.337    -.5812249    .1991571
       ced16 |  -.3029544   .1964512    -1.54   0.123     -.688318    .0824091
       ced17 |  -.0113933   .1994526    -0.06   0.954    -.4026443    .3798577
       ced18 |   .3979938   .1970337     2.02   0.044     .0114877    .7844999
       ced19 |  -.3888902   .1986962    -1.96   0.051    -.7786574     .000877
       ced20 |  -.3808243   .1996346    -1.91   0.057    -.7724324    .0107838
       ced21 |   .4754037   .1983009     2.40   0.017     .0864117    .8643956
       ced22 |  -.3342633   .1979945    -1.69   0.092    -.7226541    .0541276
       ced23 |  -.2890499   .1967737    -1.47   0.142    -.6750459    .0969461
       ced24 |   .7414483   .1978522     3.75   0.000     .3533366     1.12956
       ced25 |   .0208998   .1962026     0.11   0.915    -.3639759    .4057755
       ced26 |  -.2802188   .1992561    -1.41   0.160    -.6710844    .1106468
       ced27 |  -.2037673   .2019207    -1.01   0.313    -.5998598    .1923251
       ced28 |   -.886426   .1967576    -4.51   0.000     -1.27239   -.5004615
       ced29 |   .9150161   .1997198     4.58   0.000     .5232408    1.306791
       ced30 |   .1505522   .1996938     0.75   0.451    -.2411719    .5422764
       ced31 |   .0338336    .204322     0.17   0.869    -.3669694    .4346365
       ced32 |  -.2727766   .1970444    -1.38   0.166    -.6593036    .1137504
       ced33 |   1.116763   .1987298     5.62   0.000       .72693    1.506596
       ced34 |   .8830361    .197432     4.47   0.000     .4957487    1.270324
       ced35 |   .2703462   .1977387     1.37   0.172    -.1175428    .6582352
       ced36 |   .0104498   .1972876     0.05   0.958    -.3765544     .397454
       ced37 |  -.4834816   .1993893    -2.42   0.015    -.8746085   -.0923547
       ced38 |  -.7100399   .1965941    -3.61   0.000    -1.095684   -.3243962
       ced39 |  (omitted)
       ced40 |    .198035   .1963542     1.01   0.313    -.1871383    .5832082
        cid1 |   1.680152   .2029079     8.28   0.000     1.282123    2.078181
        cid2 |  -.1178891   .2007464    -0.59   0.557    -.5116781    .2758998
        cid3 |   .3834953   .2058763     1.86   0.063    -.0203566    .7873472
        cid4 |   1.526394   .2034908     7.50   0.000     1.127221    1.925566
        cid5 |   .6636691   .2025088     3.28   0.001      .266423    1.060915
        cid6 |    .123873   .1998081     0.62   0.535    -.2680755    .5158215
        cid7 |   .1817594   .1993881     0.91   0.362    -.2093651    .5728839
        cid8 |   .2205046   .2089568     1.06   0.291    -.1893901    .6303994
        cid9 |   .2764433   .1992735     1.39   0.166    -.1144564    .6673429
       cid10 |   .1159431   .1992318     0.58   0.561    -.2748747     .506761
       cid11 |   .1272816   .2017003     0.63   0.528    -.2683786    .5229418
       cid12 |   .1406299   .2038587     0.69   0.490    -.2592642     .540524
       cid13 |    1.46582   .2017388     7.27   0.000     1.070084    1.861556
       cid14 |  -.0078626   .1993992    -0.04   0.969    -.3990089    .3832838
       cid15 |    .364058    .203114     1.79   0.073    -.0343753    .7624914
       cid16 |   .1078348   .2018047     0.53   0.593    -.2880302    .5036999
       cid17 |   .2382488   .1991692     1.20   0.232    -.1524464    .6289439
       cid18 |    .230515   .1994864     1.16   0.248    -.1608024    .6218323
       cid19 |   .5098527   .2072802     2.46   0.014     .1032468    .9164585
       cid20 |  -.3389257   .1992385    -1.70   0.089    -.7297569    .0519054
       cid21 |   1.754684   .2015199     8.71   0.000     1.359378    2.149991
       cid22 |   .0106125   .2004059     0.05   0.958    -.3825087    .4037336
       cid23 |  -.0698658    .199243    -0.35   0.726    -.4607058    .3209742
       cid24 |   .9934234   .2017215     4.92   0.000     .5977216    1.389125
       cid25 |  -.0952417   .1993355    -0.48   0.633    -.4862632    .2957797
       cid26 |   .3526411   .2113739     1.67   0.095     -.061995    .7672773
       cid27 |   1.892756   .2044776     9.26   0.000     1.491648    2.293864
       cid28 |  -.3546606   .2017692    -1.76   0.079    -.7504559    .0411347
       cid29 |   1.177096   .2013695     5.85   0.000     .7820845    1.572107
       cid30 |   .1004037   .2004709     0.50   0.617    -.2928449    .4936523
       cid31 |   1.255257   .2028449     6.19   0.000     .8573513    1.653162
       cid32 |    .142753   .2003897     0.71   0.476    -.2503363    .5358422
       cid33 |   1.354079   .2014154     6.72   0.000     .9589778    1.749181
       cid34 |   1.397366   .2020603     6.92   0.000        1.001    1.793733
       cid35 |   .1029397    .199289     0.52   0.606    -.2879904    .4938697
       cid36 |   .6433019    .200675     3.21   0.001      .249653    1.036951
       cid37 |  (omitted)
       cid38 |  -.3321485   .2004144    -1.66   0.098    -.7252863    .0609892
       cid39 |   .8115608   .2044609     3.97   0.000     .4104853    1.212636
       cid40 |   .2613272   .1993011     1.31   0.190    -.1296268    .6522811
       _cons |   5.531002   .3406908    16.23   0.000     4.862695     6.19931
------------------------------------------------------------------------------

. 
. clear

. log close
      name:  <unnamed>
       log:  Z:\home\pacha\github\advanced-international-trade\first-edition\Chapt
> er-5\gravity_2.log
  log type:  text
 closed on:  19 Jun 2024, 13:41:11
----------------------------------------------------------------------------------

. 
end of do-file
```

### My code

```{r ch2_ex2}
trade_93 <- readRDS(paste0(dout, "/trade_93.rds"))

trade_93 %>%
  group_by(c_e) %>%
  summarise(freq = n()) %>%
  ungroup() %>%
  mutate(
    percent = freq / sum(freq) * 100,
    cum = cumsum(percent)
  )

trade_93 %>%
  group_by(c_i) %>%
  summarise(freq = n()) %>%
  ungroup() %>%
  mutate(
    percent = freq / sum(freq) * 100,
    cum = cumsum(percent)
  )

trade_93 <- trade_93 %>%
  mutate(
    d_border = case_when(
      l_ex == 1 & l_im == 1 ~ 0,
      l_ex == 2 & l_im == 2 ~ 0,
      TRUE ~ 1
    ),
    lnvx = log(vx),
    lndist = log(dist),
    lngdp_ce = log(gdp_ce),
    lngdp_ci = log(gdp_ci),
    lnn_vx = lnvx - lngdp_ce - lngdp_ci
  )

# some of the FEs are dropped in Stata
# the slopes are identical, which is what matters

fit_fe <- lm(
  lnn_vx ~ lndist + d_border + as.factor(c_e) + as.factor(c_i),
  data = trade_93
)

summary(fit_fe)
```
